---
title: "course 6 proj part 2"
author: "Viraj Bhalala"
date: "April 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(datasets)
data(ToothGrowth)
```

## Course 6 project part 2


we're going to analyze the ToothGrowth data in the R datasets package.

1. Load the ToothGrowth data and perform some basic exploratory data analyses
2. Provide a basic summary of the data.
3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
4. State your conclusions and the assumptions needed for your conclusions.

```{r cars}
library(datasets)
data(ToothGrowth)
library(ggplot2)
ggplot(ToothGrowth, aes(x=factor(dose), y=len, fill=factor(dose)))+geom_boxplot()+facet_grid(.~supp)+ggtitle("Analyzing ToothGrowth data")



```

```{r summary}
summary(ToothGrowth)


```



```{r calculate CI}
xBar<-mean(ToothGrowth$len[1:30])
yBar<-mean(ToothGrowth$len[31:60])
xVar<-(sd(ToothGrowth$len[1:30]))^2
yVar<-(sd(ToothGrowth$len[31:60]))^2
q<-(((xVar+yVar)/30)^2)/((((xVar/30)^2)+((yVar/30)^2))/29)
t<-qt(0.975, q)
yBar -xBar + c(-1,1)*t*sqrt(xVar/30 + yVar/30)


```


Perform Hypothesis test


```{r Perform hypothesis }
t.test(len~supp, data=ToothGrowth, paired=FALSE)


```


Hypothesis test for subset a
```{r Perform hypothesis 2}
a<-subset(ToothGrowth, dose==0.5)
b<-subset(ToothGrowth, dose==1.0)
c<-subset(ToothGrowth, dose==2.0)
t.test(len~supp, data=a, paired=FALSE)


```

Hypothesis test for subset b

```{r Perform hypothesis 3}
t.test(len~supp, data=b, paired=FALSE)


```
Hypothesis test for subset c
```{r Perform hypothesis 4}
t.test(len~supp, data=c, paired=FALSE)


```


##conclusion

By running this test, we founded that as tooth size increases, the doses tend to be higher 


